---
title: "An Example LaTeX Article with RMarkdown"
author: "Christopher Gandrud"
date: "12/29/2018"
output: bookdown::pdf_document2
bibliography: 
- main.bib
- packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = 'center',
                      out.width = '60%')

# pkg_to_install is created in 00-setup.Rmd
pkg_to_cite <- c("rmarkdown", "ggplot2", "rio")

# generate a BibTeX database automatically for some R packages
knitr::write_bib(pkg_to_cite, 'packages.bib')
```

\begin{abstract}
    Here is an example of a knit-able article class LaTeX document.
\end{abstract}

```{r DemPlot, echo=FALSE, warning=FALSE, fig.cap='Mean UDS Scores vs. Fertilizer Consumption'}
# Run source code to create scatter plot
source("analysis/scatter-uds-fert.R")
```

# The Graph

I gathered data from [@Pemstein2010] on countries' democracy level. They
call their democracy measure the Unified Democracy Score (UDS). I also gathered
data from the [@WorldBank2013] on fertilizer consumption.[^fert_explain] Figure \@ref(fig:DemPlot) shows the mean UDS scores over time for all of the countries in their sample plotted against the natural logarithm of their fertilizer consumption.

# Appendix

This document was created using the R version `r paste0(version$major, '.', version$minor)` 
and the R package
*rmarkdown* [@R-rmarkdown]. It also relied on the R packages *ggplot2*
[@R-ggplot2] and *rio* [@R-rio]. The document can be
completely reproduced from source files available on GitHub at:
<https://github.com/christophergandrud/rep-res-book-v3-examples>.

The R session info is:

```{r SessionInfo, echo=FALSE, results='asis'}
toLatex(sessionInfo())
```

# References


[^fert_explain]: The data is in kilograms per hectare of arable land.